Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-23 journal/article.tex
S: No top-down mandate

>>>>

% No top-down mandate

An interesting success factor was the absence of a top-down mandate. Atlas [P3]
describes that the use of Scrum was spreading because teams were both allowed to
use and enabled to learn the method. The transformation itself was agile when
people felt empowerment in making the decision to adopt. The incentive to change
was created when teams learned about agile methods, and perceived that a change
would be beneficial [P3].
The absence of mandate granted genuine support for the model on the grass roots
level, which was a necessity for the process to work [P6].
It was also thought that proceeding with a top-down mandate would have made
teams use a uniform process [P41]. This would have been suboptimal, as it was
important that the practices were tailored for each team and project [P41].
